Phenotype and risk assessment of insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-10-16 analysis/paper/paper.Rmd
Introduction checked

@@

Based on the severity and symptom profile, we defined a sub-elevated baseline serum tryptase (BST) cut-off value of 8 - 11.5 ng/ml (Fig. \@ref(fig:figcofactors)B).

@@

We trained a random forest classifier (using the "randomForest" package for R [@rf]) in order to find therapeutic approaches that varied the most between VIA / non-VIA group and presented the results Gini importance [@Strobl2007]. We also performed an association study of therapeutic interventions and symptoms. The resulting phi values are presented in a heatmap with automatic clustering using Ward’s Agglomerative Hierarchical Clustering with Euclidean distances [@heatmaply].

>>>>

Anaphylaxis is a clinical diagnosis with a variety of trigger factors and clinical presentations. Symptom profiles and specific cofactors for venom induced anaphylaxis had previously been analysed in uncontrolled manner in relatively small cohorts [@LANTNER; @Ruff2009; @nittner2015insect].

@@

Based on the severity and symptom profile, we defined sub-elevated baseline serum tryptase (BST) values as 8 - 11.5 ng/ml (Fig. \@ref(fig:figcofactors)B).

@@

We trained a random forest classifier (using the "randomForest" package for R [@rf]) in order to find therapeutic approaches that varied the most between VIA / non-VIA group and presented the results as Gini importance [@Strobl2007]. We also performed an association analysis of therapeutic interventions and symptoms. The resulting phi values are presented in a heatmap with automatic clustering using Ward’s Agglomerative Hierarchical Clustering with Euclidean distances [@heatmaply].
